Augraphy: An Augmentation Pipeline API for Modern Document Images

### 2023-01-25 paper.tex

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage[colorlinks]{hyperref}
\hypersetup{
    colorlinks = false,
    linkbordercolor = {blue}
}
\usepackage{listings}
\usepackage{courier}
\usepackage{booktabs}
\usepackage[dvipsnames]{xcolor}
\usepackage{amssymb}
\usepackage{pifont}
\usepackage{listings}
\usepackage{times}
\renewcommand{\floatpagefraction}{.8}

@@

>>>>

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage[colorlinks]{hyperref}
\hypersetup{
    colorlinks = false,
    linkbordercolor = {blue}
}
\usepackage{listings}
\usepackage{courier}
\usepackage{booktabs}
\usepackage[dvipsnames]{xcolor}
\usepackage{amssymb}
\usepackage{pifont}
\usepackage{listings}
\usepackage{times}
\usepackage{wrapfig}
\renewcommand{\floatpagefraction}{.8}

@@

\subsection{Face Detection Robustness Testing}

In this section, we use \emph{Augraphy} to investigate the robustness of face detection models on images that have been altered by \emph{Augraphy}.
In this way, we move beyond analyzing robustness of text-related tasks, but the images we analyze in this section can nonetheless appear in documents like newspapers, which are often scanned from the physical world by noisy scanners.
Hence, it is important for image-focused models like image classifiers and object detection models to be robust to scanner-induced noise.

\begin{wraptable}{r}{5cm}
    \centering
    \caption{Face detection performance.}
    \begin{tabular}{lr}
    \toprule
        \textbf{Model} & \textbf{Accuracy} \\
        \midrule
        Azure & 57.1\%\\
        Google & 60.1\%  \\
        Amazon & 49.1\% \\
        UltraFace & 4.5\%\\
        \bottomrule
    \end{tabular}
    \label{tab:face-detection-results}
\end{wraptable}

We begin by sampling 75 images from the FDDB face detection benchmark \cite{fddbTech}.
Then, we use \emph{Augraphy} to generate 10 altered versions of each image and manually remove any augmented image where the face(s) is not reasonably visible.
We then test four face detection models on the noisy and noise-free images.
These models are: proprietary face detection models from Google,\footnote{\url{https://cloud.google.com/vision/docs/detecting-faces}} Amazon,\footnote{\url{https://aws.amazon.com/rekognition/}} and Microsoft\footnote{\url{https://azure.microsoft.com/en-us/services/cognitive-services/face}}, and lastly the freely-available UltraFace\footnote{\url{https://github.com/onnx/models/tree/main/vision/body_analysis/ultraface}} model.
%We then test Microsoft Azure's face detection model on the noise-free and noisy images.

Table~\ref{tab:face-detection-results} shows face detection accuracy of both models on the noisy test set, and example images where no faces were detected by the Microsoft model are shown in Figure \ref{fig:face-detection-mistakes}.
We see that all four models struggle on the \emph{Augraphy}-augmented data, with the proprietary models seeing detection performances drop to between roughly 50-60\%, and UltraFace detecting only 4.5\% of faces that it found in the noise-free data.

\begin{figure}
    \centering\scalebox{0.47}{
    \includegraphics{figures/azure_1x3_face_errors.pdf}}
    \caption{Example augmented images that yielded false-positive predictions with the Azure face detector.}
    \label{fig:face-detection-mistakes}
\end{figure}
